Defining properties regulating pioneer-factor binding and function

### 2023-02-13 manuscript/manuscript_sections/_06_Figure_Legends.qmd
update MS text

**Extended Data Figure 2: Zld and Grh bind to chromatin rapidly after induction of protein expression**

-   ~~Western blot time course of protein levels~~

-   CUT&RUN time course to show rapid binding

-   likely rules out dependence on DNA replication

**Extended Data Figure 3: Ectopic expression of pioneer factors in S2 cells leads to widespread changes to chromatin accessibility and gene expression.**

-   volcano and/or MA plots with enrichment of binding

-   Analysis of nonspecific changes?

-   ~~RNA-seq volcano/MA plots~~

-   ~~RNA-seq GO analysis~~

>>>>

**Extended Data Figure 2: Zld and Grh bind to chromatin rapidly after induction of protein expression. a-b,** Immunoblots showing time course of Zld **(a)** or Grh **(b)** protein expression following induction of stable cell lines.
**c-d,** Metaplots showing average z-score normalized CUT&RUN signal at class I, II or III sites at different time points following induction.

**Extended Data Figure 3: Ectopic expression of pioneer factors in S2 cells leads to widespread changes to chromatin accessibility and gene expression. a,d,** Volcano plots showing changes in ATAC-seq signal in cells expressing Zld **(a)** or Grh **(d)** when compared to WT cells treated with the same concentration of CuSO~4~.
**b,e,** RNA-seq volcano plots showing gene expression changes in cells expressing Zld **(a)** or Grh **(d)** when compared to WT cells treated with the same concentration of CuSO~4~.
**c,f,** Bar plots showing enrichment of gene ontology terms in genes significantly upregulated upon expression of Zld **(c)** or Grh **(f)**.
